Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-20 ApproximateCode.tex

\subsection{Existing Erasure Codes}\label{existEC}
Reliability is a critical issue since disk failures are typical in storage systems. To improve the reliability of storage systems, several RAID forms (e.g., RAID-5, RAID-6, 3DFTs) and erasure codes are proposed by researchers.  Traditional erasure codes can be categorized into two classes, Maximum Distance Separable (MDS) codes and non-MDS codes. MDS codes aim to offer data protection with optimal storage efficiency. On the other hand, non-MDS codes improve the performance or reliability by consuming extra storage space.

In the past two decades, several
famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code [CITE], RDP code [CITE], Blaum-Roth code[CITE], X-code [CITE], Liberation code [CITE], Liber8tion code [CITE], Cyclic [CITE] code, B-Code [CITE], Code-M [CITE], H-code [CITE], P-code [CITE] and HVcode [CITE], etc.

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [CITE], Cauchy-RS codes [CITE], STAR code [CITE], Triple-Star code [CITE], Triple-Parity code [CITE], HDD1 code [CITE], RSL-code [CITE], RL-code [CITE], and so on. Typical non-MDS codes contain WEAVER codes [CITE], HoVer
codes [CITE], T-code [CITE], HDD2 code [CITE], Pyramid codes [CITE], Local Reconstruction Codes [CITE], Locally Repairable Codes [CITE], etc.

Several classic erasure codes are illustrated in detail as below,

>>>>

\subsection{Existing Erasure Codes}\label{existEC}

Reliability is a critical issue since disk failures are typical in storage systems. To improve the reliability of storage systems, several RAID forms (e.g., RAID-5, RAID-6, 3DFTs) and erasure codes are proposed by researchers.  Traditional erasure codes can be categorized into two classes, Maximum Distance Separable (MDS) codes and non-MDS codes. MDS codes aim to offer data protection with optimal storage efficiency. On the other hand, non-MDS codes improve the performance or reliability by consuming extra storage space.

In the past two decades, several famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code \cite{EVENODD}, RDP code \cite{RDP}, Blaum-Roth code\cite{BlaumRoth}, X-code \cite{XCode}, Liberation code \cite{Liberation}, Liber8tion code \cite{Liber8tion}, Cyclic \cite {Cyclic} code, B-Code \cite{BCode}, Code-M \cite{Code-M}, H-code \cite{hcode}, P-code \cite{PCode} and HVcode \cite{HVCode}, etc.

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, RL-code \cite{RL}, and so on. Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.

Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating. Several attempts have been made to address this issue. Local Construction Code (LRC) \cite{LRC} is one of these attempts which succeeds in reducing the bandwidth and I/Os required for repair reads at the expense of higher storage overhead.

Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures. This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed. XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures. More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.

STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code. It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
\begin{figure}[!ht]
 \centering
 \subfigure[Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
 }
 \hspace{5pt}
 \subfigure[Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
 } \\
 \subfigure[Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
 }
 \hspace{5pt}
 \caption{Encoding of STAR code ($p = 5$).}
 \label{fig:star-enc}
\end{figure}

TIP-code \cite{tip} is a solution for p or p+1 disks, where p is a prime number. Compared to STAR, Tip's input of the diagonal and anti-diagonal parity is modified so they are evenly distributed among all the data blocks. This minor modification has enabled TIP-code to achieve optimal update complexity.
